---
title: "Additional Analyses"
output: 
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
    code_folding: hide
---

```{r setup, include=F}
knitr::opts_chunk$set(
  cache = TRUE
  , comment = NA
  , warning = FALSE
  , echo = TRUE
  , error = FALSE
  , message = FALSE
  , prompt = FALSE
  , tidy = TRUE
  , fig.height = 4
  )

options(
  digits = 3
  , width = 120
  )
```

In what follows, please find the results of additional analyses. These include models, results without covariates, results with all participants (hence, including those removed due to speeding).

# Set-up

Load packages.

```{r r-setup, results='hide', cache=F}
# define packages
packages <- 
  c(
    "cowplot"
    , "devtools"
    , "faoutlier"
    , "GGally"
    , "kableExtra"
    , "knitr"
    , "lavaan"
    , "magrittr"
    , "MVN"
    , "psych"
    , "pwr"
    , "quanteda"
    , "semTools"
    , "td"
    , "tidyverse"
    )

# load packages
lapply(
  packages
  , library
  , character.only = TRUE
  , quietly = TRUE
  )
```

Load data.

```{r Data-Wrangling, cache=F}
# load workspace
load("data/workspace.rdata")
```

# VIF

In what follows, you can find estimations of variance inflation factors, which help gauge multicollinearity. Generally, values above 5 or even 10 are considered problematic. However, these are only rules of thumb, and multicollinearity can occur with lower values. Indeed, although the values reported below are not above 5, they are increased, suggesting that multicollinearity might be at play here, which the preregistered analyses also confirm.

```{r vif}
# Self-Efficacy
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
SE01_01 ~~ a*SE01_02
SE01_03 ~~ a*SE01_04
trust_community =~ TR01_01 + TR01_02 + TR01_03
trust_provider =~ TR01_04 + TR01_05 + TR01_06 + TR01_07 + TR01_08 + TR01_09
trust_spec =~ trust_community + trust_provider

self_eff ~ pri_con + grats_gen + pri_delib + trust_spec

# Covariates
GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_01 + TR01_02 + TR01_03 + TR01_04 + TR01_05 + TR01_06 + TR01_07 + TR01_08 + TR01_09 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit <- sem(model, data = d, estimator = "MLR", missing = "ML")
r_self_eff <- inspect(fit, what = "rsquare")["self_eff"] # extract rsquare
vif_self_eff <- 1 / (1 - r_self_eff) # compute vif

# Privacy Deliberation
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
SE01_01 ~~ a*SE01_02
SE01_03 ~~ a*SE01_04
trust_community =~ TR01_01 + TR01_02 + TR01_03
trust_provider =~ TR01_04 + TR01_05 + TR01_06 + TR01_07 + TR01_08 + TR01_09
trust_spec =~ trust_community + trust_provider
pri_delib ~ self_eff + pri_con + grats_gen + trust_spec

# Covariates
GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_01 + TR01_02 + TR01_03 + TR01_04 + TR01_05 + TR01_06 + TR01_07 + TR01_08 + TR01_09 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit <- sem(model, data = d, estimator = "MLR", missing = "ML")
r_pri_delib <- inspect(fit, what = "rsquare")["pri_delib"]
vif_pri_delib <- 1 / (1 - r_pri_delib)

## Privacy Concerns
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
SE01_01 ~~ a*SE01_02
SE01_03 ~~ a*SE01_04
trust_community =~ TR01_01 + TR01_02 + TR01_03
trust_provider =~ TR01_04 + TR01_05 + TR01_06 + TR01_07 + TR01_08 + TR01_09
trust_spec =~ trust_community + trust_provider

pri_con ~ self_eff + pri_delib + grats_gen + trust_spec

# Covariates
GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_01 + TR01_02 + TR01_03 + TR01_04 + TR01_05 + TR01_06 + TR01_07 + TR01_08 + TR01_09 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit <- sem(model, data = d, estimator = "MLR", missing = "ML")
r_pri_con <- inspect(fit, what = "rsquare")["pri_con"]
vif_pri_con <- 1 / (1 - r_pri_con)

# Gratifications
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
SE01_01 ~~ a*SE01_02
SE01_03 ~~ a*SE01_04
trust_community =~ TR01_01 + TR01_02 + TR01_03
trust_provider =~ TR01_04 + TR01_05 + TR01_06 + TR01_07 + TR01_08 + TR01_09
trust_spec =~ trust_community + trust_provider
grats_gen ~ self_eff + pri_con + pri_delib + trust_spec

# Covariates
GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_01 + TR01_02 + TR01_03 + TR01_04 + TR01_05 + TR01_06 + TR01_07 + TR01_08 + TR01_09 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit <- sem(model, data = d, estimator = "MLR", missing = "ML")
r_grats_gen <- inspect(fit, what = "rsquare")["grats_gen"]
vif_grats_gen <- 1 / (1 - r_grats_gen)

# Trust
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
SE01_01 ~~ a*SE01_02
SE01_03 ~~ a*SE01_04
trust_community =~ TR01_01 + TR01_02 + TR01_03
trust_provider =~ TR01_04 + TR01_05 + TR01_06
trust_system =~ TR01_07 + TR01_08 + TR01_09
trust_spec =~ trust_community + trust_provider + trust_system

trust_spec ~ self_eff + pri_con + grats_gen + pri_delib

# Covariates
GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_01 + TR01_02 + TR01_03 + TR01_04 + TR01_05 + TR01_06 + TR01_07 + TR01_08 + TR01_09 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit <- sem(model, data = d, estimator = "MLR", missing = "ML")
r_trust_spec <- inspect(fit, what = "rsquare")["trust_spec"]
vif_trust_spec <- 1 / (1 - r_trust_spec)
```

```{r}
# Table
tibble("Gratifications" = vif_grats_gen, "Trust Specific" = vif_trust_spec, "Privacy Concerns" = vif_pri_con, "Privacy Deliberation" = vif_pri_delib, "Self-Efficacy" = vif_self_eff) %>% 
  kable() %>% 
  kable_styling("striped")
```

# Preregistered model

I first analyze the model how it was initially preregistered.

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
trust_community =~ TR02_01 + TR01_01 + TR01_02 + TR01_03
trust_provider =~ TR02_02 + TR01_04 + TR01_05 + TR01_06
trust_system =~ TR02_03 + TR01_07 + TR01_08 + TR01_09
trust =~ trust_community + trust_provider + trust_system

self_dis_log ~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust

# Covariates
self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR02_01 + TR02_02 + TR02_03 + TR01_01 + TR01_02 + TR01_03 + TR01_04 + TR01_05 + TR01_06 + TR01_07 + TR01_08 + TR01_09 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit_prereg <- sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit_prereg, fit = TRUE, std = TRUE)
rsquare_fit_prereg <- inspect(fit_prereg, what = "rsquare")["self_dis_log"]
```

First, first is not optimal but still okaish, `r td::fit_txt(fit_prereg)`. The result show the same problems of multicollinearity, namely that trust reduces online communication (despite a positive and more "plausible" postive bivariate relation).

# Results without covariates

As stated in our preregistration, we also provide the results without controlling for covariates. Note were here now using the updated preregistered model as reported in the paper.

```{r}
model <- "
  pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
  grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
  pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
  self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
  trust_community =~ TR01_01 + TR01_02 + TR01_03
  trust_provider =~ TR01_04 + TR01_05 + TR01_06
  trust_system =~ TR01_07 + TR01_08 + TR01_09
  trust_spec =~ trust_community + trust_provider + trust_system

words_log ~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec
"
fit_prereg <- sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit_prereg, fit = TRUE, std = TRUE)
rsquare_fit_prereg <- inspect(fit_prereg, what = "rsquare")["comm"]
```

The results remain virtually the same (see page [analyses](analyses.html)).

# Results including removed participants

As stated in the preregistration, we also report the analyses including the deleted participants.

We first need to rerun the baseline model to get new factor scores (output not shown here).

```{r results='hide'}
model_baseline <- "
  pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
  grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
  grats_inf =~ GR01_01 + GR01_02 + GR01_03 
  grats_rel =~ GR01_04 + GR01_05 + GR01_06 
  grats_par =~ GR01_07 + GR01_08 + GR01_09
  grats_ide =~ GR01_10 + GR01_11 + GR01_12 
  grats_ext =~ GR01_13 + GR01_14 + GR01_15
  grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
  pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
  trust_gen =~ TR02_01 + TR02_02 + TR02_03
  trust_community =~ TR01_01 + TR01_02 + TR01_03
  trust_provider =~ TR01_04 + TR01_05 + TR01_06
  trust_system =~ TR01_07 + TR01_08 + TR01_09
  trust_spec =~ trust_community + trust_provider + trust_system
  self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
    SE01_01 ~~ x*SE01_02
    SE01_03 ~~ x*SE01_04
  Words_log =~ words_log
  
  Words_log ~~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec + f1*trust_gen + g1*grats_spec
"
fit_baseline <- sem(model_baseline, data = d_all, missing = "ML")
summary(fit_baseline, standardized = TRUE, fit.measures = TRUE)
```

```{r results='hide'}
# extract model predicted values for items & calc means
d_fs <- lavPredict(fit_baseline, type = "ov") %>% 
  as.data.frame() %>% 
  mutate(version = d_all$version, 
         grats_gen_fs = rowMeans(select(., starts_with("GR02"))),
         grats_spec_fs = rowMeans(select(., starts_with("GR01"))), 
         pri_con_fs = rowMeans(select(., starts_with("PC01"))),
         trust_gen_fs = rowMeans(select(., TR02_01, TR02_02, TR02_03)),
         trust_spec_fs = rowMeans(select(., TR01_01: TR01_09)),
         pri_del_fs = rowMeans(select(., starts_with("PD01"))),
         self_eff_fs = rowMeans(select(., starts_with("SE01")))) %>%
  select(version, pri_con_fs, grats_gen_fs, grats_spec_fs, pri_del_fs, self_eff_fs, trust_gen_fs, trust_spec_fs, words_log)

# combine d with d factor scores
d_all %<>% cbind(select(d_fs, -version, -words_log))
```

Let's now inspect the results of the (updated) preregistered model including removed cases.

```{r}
model <- "
  pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
  grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
  pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
  self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
  trust_community =~ TR01_01 + TR01_02 + TR01_03
  trust_provider =~ TR01_04 + TR01_05 + TR01_06
  trust_system =~ TR01_07 + TR01_08 + TR01_09
  trust_spec =~ trust_community + trust_provider + trust_system

words_log ~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec

# Covariates
words_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_01 + TR01_02 + TR01_03 + TR01_04 + TR01_05 + TR01_06 + TR01_07 + TR01_08 + TR01_09 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu

# Covariances
male ~~ age + edu
age ~~ edu
"
fit_prereg <- sem(model, data = d_all, estimator = "MLR", missing = "ML")
summary(fit_prereg, fit = TRUE, std = TRUE)
```

First, we can see that the analyses now include the data of 590 participants. However, when comparing the analyses, we see that results don't differ in any meaningful way.